---
title: "AbSeq analysis report"
output:
    html_document:
        toc: true
        toc_float:
            collapsed: false
            smooth_scroll: false
params:
    singleSamples: "PCR1,PCR2,PCR3"
    multiSamples: "PCR1_vs_PCR2,PCR1_vs_PCR3,PCR1_vs_PCR5,PCR2_vs_PCR3"
    singleSampleLinks: "link1,link2,link3"
    multiSampleLinks: "link12,link13,link14,link15"
    chains: "hv,lv,hv"
    rawReads: "1000,1000,1000"
    annotReads: "900, 291, 987"
    prodReads: "500, 200, 123"
    filters: "bitscore: 1 - inf, alignlen: 1 - inf, sstart: 1 - inf, qstart: 1 - inf ? bitscore: 1 - inf, alignlen: 1 - inf, sstart: 1 - inf, qstart: 1 - inf ? bitscore: 1 - inf, alignlen: 1 - inf, sstart: 1 - inf, qstart: 1 - inf "
    filterSplitter: "?"
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)

.formatNumber <- function(numStr, denom) {
    n <- suppressWarnings(as.numeric(numStr))
    d <- suppressWarnings(as.numeric(denom))
    nStr <- prettyNum(n, big.mark = ",")
    dStr <- prettyNum(d, big.mark = ",")
    perc <- n / d * 100
    return(sprintf("%s%% (%s/%s)", round(perc, 2), nStr, dStr))
}
```

This report is generated on `r format(Sys.time(), "%a %b %d %X %Y")`

<!-- number of samples:, indv, comp -->
# Summary

Individual samples are listed in the following table with a brief summary.

The comparative analysis (if any) will appear [after the table](#comparative-reports).

## Samples

Number of samples: `r length(unlist(strsplit(params$singleSampleLinks, ",")))`


```{r echo=FALSE}
samples <- unlist(strsplit(params$singleSamples, ","))
links <- unlist(strsplit(params$singleSampleLinks, ","))
chains <- unlist(strsplit(params$chains, ","))
rawReads <- unlist(strsplit(params$rawReads, ","))
annotReads <- unlist(strsplit(params$annotReads, ","))
prodReads <- unlist(strsplit(params$prodReads, ","))
filters <- unlist(strsplit(params$filters, params$filterSplitter, fixed = T))
if (length(samples) * 7 != (length(samples) + length(links) + length(chains) + length(rawReads) + length(annotReads) + length(prodReads)) + length(filters)) {
    stop("Expected same argument length for singleSamples, chains, rawReads, annotReads, prodReads and filters")
}
singleTableInfo <- lapply(seq_along(samples), function(i) {
    reads <- prettyNum(rawReads[i], big.mark = ",")
    annots <- .formatNumber(annotReads[i], rawReads[i])
    prods <- .formatNumber(prodReads[i], annotReads[i])
    filts <- gsub(",", "<br>", filters[i], fixed = T)
    knitr::knit_expand(text = sprintf("[%s](%s) | %s | %s | %s | %s | %s", samples[i], links[i], chains[i], reads, annots, prods, filts))
})
```
sample | chain | # reads | annotated reads | productive reads | filters applied
-------|-------|---------|-----------------|------------------|----------------
`r paste(knitr::knit(text = paste(singleTableInfo, collapse = '\n')))`

## Comparative reports

Number of comparative reports: `r length(unlist(strsplit(params$multiSampleLinks, ",")))`

```{r echo=FALSE}
samples <- unlist(strsplit(params$multiSamples, ","))
links <- unlist(strsplit(params$multiSampleLinks, ","))
if (length(samples) != length(links)) {
    stop("Expected equal number of samples and links")
}

comparativePoints <- lapply(seq_along(samples), function(i) {
    knitr::knit_expand(text = sprintf("* [%s](%s)", samples[i], links[i]))
})
```

`r paste(knitr::knit(text = paste(comparativePoints, collapse = '\n')))`

<!-- R, py version - R, py packages -->
# Additional information
